Conformal Counterfactual Explanations

### 2023-03-23 paper/paper.tex
progress

\begin{definition}[Conformal Counterfactuals]
  \label{def:conformal}
  Let $\mathcal{X}_{\theta}|y=t = p_{\theta}(x|y=t)$ denote the conditional distribution of $x$ in the target class $t$, where $theta$ denotes the parameters of model $M$. Then for $x^{\prime}$ to be considered a conformal counterfactual, we need: $x^{\prime} \sim \mathcal{X}_{\theta}|y=t$.
\end{definition}

@@

>>>>

\begin{definition}[Conformal Counterfactuals]
  \label{def:conformal}
  Let $\mathcal{X}_{\theta}|t = p_{\theta}(x|y=t)$ denote the conditional distribution of $x$ in the target class $t$, where $theta$ denotes the parameters of model $M$. Then for $x^{\prime}$ to be considered a conformal counterfactual, we need: $x^{\prime} \sim \mathcal{X}_{\theta}|t$.
\end{definition}

@@

\subsection{Conformal Training meets Counterfactual Explanations}

\section{Experiments}
